Space is the Place: Effects of Continuous Spatial Structure on Analysis of Population Genetic Data

### 2019-12-06 ms/spaceness.tex
bibtex fixes

The inescapable reality that biological organisms live, move, and reproduce in continuous geography is usually omitted from population genetic models. However, mates tend to live near to one another and to their offspring, leading to a positive correlation between genetic differentiation and geographic distance. This pattern of ``isolation by distance'' \citep{Wright1943} is one of the most widely replicated empirical findings in population genetics \citep{Chen2017,Jay2012,Sharbel2000}.
Despite a long history of analytical work describing the genetics of populations distributed across continuous geography
(e.g., \citet{Wright1943,Rousset1997,barton2002neutral,Barton2010,Ringbauer2017,robledoarnuncio2010isolation,Wilkins2002linearcoalescent,Wilkins2004separation}), \revpoint{AE}{1}
much modern work still describes geographic structure as a set of discrete populations connected by migration \citep[e.g.,][]{Wright1931,epperson2003geographical,rousset2011likelihoodbased,Shirk2014,lundgren2019populations} or as an average over such discrete models \citep{Petkova2015,al2019estimating}. \revpoint{4}{3}
For this reason, most population genetics statistics are interpreted with reference to discrete, well-mixed populations, and most empirical papers analyze variation within clusters of genetic variation inferred by programs like \textit{STRUCTURE} \citep{Pritchard2000} with methods that assume these are randomly mating units.

>>>>

The inescapable reality that biological organisms live, move, and reproduce in continuous geography is usually omitted from population genetic models. However, mates tend to live near to one another and to their offspring, leading to a positive correlation between genetic differentiation and geographic distance. This pattern of ``isolation by distance'' \citep{Wright1943} is one of the most widely replicated empirical findings in population genetics \citep{Chen2017,Jay2012,Sharbel2000}.
Despite a long history of analytical work describing the genetics of populations distributed across continuous geography
(e.g., \citet{Wright1943,Rousset1997,barton2002neutral,Barton2010,Ringbauer2017,robledoarnuncio2010isolation,Wilkins2002linearcoalescent,wilkins2004separation}), \revpoint{AE}{1}
much modern work still describes geographic structure as a set of discrete populations connected by migration \citep[e.g.,][]{Wright1931,epperson2003geographical,rousset2011likelihoodbased,Shirk2014,lundgren2019populations} or as an average over such discrete models \citep{Petkova2015,al2019estimating}. \revpoint{4}{3}
For this reason, most population genetics statistics are interpreted with reference to discrete, well-mixed populations, and most empirical papers analyze variation within clusters of genetic variation inferred by programs like \textit{STRUCTURE} \citep{Pritchard2000} with methods that assume these are randomly mating units.
